---
title: "Week 1 Exercise: Introduction to R and Quarto"
author: "Your Name"
date: today
format: html
---

## Overview

This exercise introduces basic R operations and the Quarto workflow.
Complete each section and render the document when finished.

---

## Part 1: Basic Calculations

R can be used as a calculator. Run the code below and check the output.

```{r}
# Population of Canada (approximate, 2024)
canada_pop <- 40_000_000

# Annual growth rate (percent)
growth_rate <- 0.9

# Project population 10 years forward
projected <- canada_pop * (1 + growth_rate / 100)^10
projected
```

**Question:** What does the `^` operator do? Try changing the growth rate and re-render.

---

## Part 2: Vectors

```{r}
# Fertility rates (children per woman) for selected countries
country <- c("Niger", "Mali", "Chad", "Canada", "Japan", "South Korea")
tfr      <- c(6.8,    5.9,    5.6,    1.5,      1.2,     0.7)

# Which countries are below replacement (TFR < 2.1)?
country[tfr < 2.1]
```

**Question:** Add one more country and its TFR to each vector. Re-render.

---

## Part 3: A Simple Plot

```{r}
# Bar chart of TFRs
barplot(
  tfr,
  names.arg = country,
  col       = "steelblue",
  las       = 2,          # rotate x-axis labels
  ylab      = "Total Fertility Rate",
  main      = "Fertility Rates by Country"
)
abline(h = 2.1, lty = 2, col = "red")  # replacement-level line
```

---

## Submission

Render this document to HTML (click **Render** or run `quarto::quarto_render("exercise01.qmd")`),
then upload the `.html` file to Canvas.
